\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-07-12 doc/USER_MANUAL/11_graphics.tex
updates surface movie and shakemap routines

\subsection{Movie Surface}

When running \texttt{xspecfem3D} with the \texttt{MOVIE\_SURFACE}
flag turned on, the code outputs \texttt{moviedata??????} files in
the \texttt{OUTPUT\_FILES} directory. There are several flags in the
main parameter file \texttt{Par\_file} that control the output of
these movie data files (see section \ref{cha:Main-Parameter} for
details):
\texttt{\small NTSTEP\_BETWEEN\_FRAMES} to set the
timesteps between frames,
\texttt{\small SAVE\_DISPLACEMENT}
to save displacement instead of velocity,
\texttt{\small USE\_HIGHRES\_FOR\_MOVIES}
to save values at all GLL point instead of element edges. In order
to output additionally shakemaps, you would set the parameter
\texttt{\small CREATE\_SHAKEMAP}
to \texttt{\small .true.}.

The files are in a fairly complicated binary format, but there is
a program provided to convert the output into more user friendly formats:
\begin{description}
\item [{\texttt{xcreate\_movie\_shakemap\_AVS\_DX\_GMT}}]
From \texttt{create\_movie\_shakemap\_AVS\_DX\_GMT.f90},
it outputs data in ASCII, OpenDX, or AVS format (also readable in
ParaView). Before compiling the code, make sure you have the file
\texttt{surface\_from\_mesher.h} in the \texttt{OUTPUT\_FILES/} directory.
This file will be created by the solver run. Then type

>>>>

\subsection{Movie Surface and Shakemaps}

When running \texttt{xspecfem3D} with the \texttt{MOVIE\_SURFACE}
flag turned on, the code outputs \texttt{moviedata??????} files in
the \texttt{OUTPUT\_FILES} directory. There are several flags in the
main parameter file \texttt{Par\_file} that control the output of
these movie data files, please see section \ref{cha:Main-Parameter} for
more details. Especially, the following parameters affect the output:
\begin{itemize}
\item \texttt{\small SAVE\_DISPLACEMENT}: to save displacement instead of velocity,
\item \texttt{\small NTSTEP\_BETWEEN\_FRAMES}: to set the timesteps between frames,
\item \texttt{\small USE\_HIGHRES\_FOR\_MOVIES}: to save values at all GLL point instead of element edges.
\end{itemize}

You can also output shakemaps independant of the \texttt{MOVIE\_SURFACE} flag. Shakemaps show the peak-ground values of the simulation. For creating shakemaps (at the end of the simulation), you would set the parameter
\texttt{\small CREATE\_SHAKEMAP} to \texttt{\small .true.}.
For shakemaps, both the parameters \texttt{\small MOVIE\_TYPE} and \texttt{\small USE\_HIGHRES\_FOR\_MOVIES} affect the output. The following setting has an additional affect:
\begin{itemize}
\item \texttt{\small MOVIE\_TYPE}: if set to $1$, the horizontal peak-ground values of displacement/velocity/acceleration are output. if set to $2$, the maximum length of the particle displacement/velocity/acceleration vector is output. Please be aware that these peak-ground values can differ from each other.
\end{itemize}

The movie and shakemap output files are in a custom binary format, but there is
a program provided to convert the output into more user friendly formats:
\begin{description}
\item [{\texttt{xcreate\_movie\_shakemap\_AVS\_DX\_GMT}}]
From \texttt{create\_movie\_shakemap\_AVS\_DX\_GMT.f90},
it outputs data in ASCII, OpenDX, or AVS format (also readable in
ParaView). Before compiling the code, make sure you have the file
\texttt{surface\_from\_mesher.h} in the \texttt{OUTPUT\_FILES/} directory.
This file will be created by the solver run. Then type
